### 2019-07-09 paper_04_shallow_water/Latex/article.tex

The shocks we observed in the SW simulations left us in a state of curiosity. In some simulations they appeared to be pretty strong and in others rather weak. In some simulations they were densely packed and in others sparsely distributed. 
In what way  do the input parameters regulate these variations? Will there always be shocks or will they disappear in the limit of weak nonlinearities?  Such questions made us to shift our theoretical focus and pursue the study, despite the fact that the answer to the question that originally motived it turned out to be negative.

@@

We have carried out a set of twenty forced-dissipative simulations of the SW
equations in a quadratic domain with periodic boundary conditions using the
standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
fluidsim}. In these twenty simulations we used an eight order diffusion operator to act as the agent of dissipation. 
 On the request from the reviewers we have also carried out a set of thirteen simulation with  Laplacian diffusion. The results from the latter set, which are similar to the results from the first set,  are presented in Appendix A.

@@

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig9}}
\caption{ Top: Flatness factor of transverse velocity increments. Bottom: Ratio between transverse and longitudinal flatness factor. Left: runs with $ n=3840 $: W3,
W7, W11,  W14 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15.  The dotted straight lines indicate the value 1.5 predicted by the shock model.  }
\label{fig9}
\end{figure}

@@

As expected, we have found that the displacement structure functions scale
exactly in the same way as the velocity structure functions, and for this reason we only plot
velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
compensated and normalised second, fourth and sixth order longitudinal
structure functions from the five simulations with $ n = 3840 $ to the left and
the three simulations with $ n = 7860 $ to the right. At small separation, $ r
< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
is characteristic of a smooth velocity field, indicating that the shocks are
reasonably well resolved. There is a small bump around the shock width, $ r
\approx \delta x $, and at $ r > \delta x $, there is a range where the
compensated structure functions are flat, or almost flat. As expected, this
range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
also broader in the higher resolution runs to the right as compared to the
lower resolution simulations to the left. There is clearly a better collapse of
the curves for the sixth order structure functions compared to the second order
structure functions. This is not surprising, since the shock contribution to
the structure functions should become increasingly dominant with increasing
order. Plots of the transverse structure functions are very similar to the
plots of the longitudinal structure functions, with the difference that the
transverse structure functions are somewhat smoother at $ r \approx \delta x $.
In figure~\ref{fig_ratio} we see the ratio $ R_{p}(r) = \langle \mid \delta
u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
2,3,4,5,6 $ from run W8, together with dotted straight lines, indicating the
values predicted by (\ref{Ratio}). As can be seen, there is a quite good
agreement with the predicted values in a limited range of separations, $ r >
\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
becomes more narrow with increasing $ p $, an observation that we cannot
explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
$ r $, which is the theoretical single point limit for an irrotational
isotropic field. In figure~\ref{fig9} we see the flatness factor, $
F_T $, of the transverse structure functions at the top and the ratio, $
F_T/F_L $, at the bottom. The figures to the left show the results from the
five simulations with $ n = 3840 $ and the figures to the right show the
results from the three simulations with $ n = 7860 $. The flatness factor shows
increasingly large values for decreasing $ r $ with a dependence that is rather
close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
is increasing with decreasing scale is by some authors defined as the most
appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
limited range of separations, $ r > \delta x $, which is becoming somewhat
broader as $ c $ is increasing and is also somewhat broader in the higher
resolution runs shown to the right as compared to the lower resolution runs
shown to the left. This is in accordance with the shock model predictions
(\ref{FL}) and (\ref{FT}).

@@

\vskip 0.5 cm

\noindent The authors would like to thank Gregory Falkovich and Sergey Nazaranko for  fruitful criticism of an early version of the manuscript and three anonymous reviewers for useful comments. Financial
support from the Swedish Research Council (VR) is gratefully
acknowledged. The simulations were performed
on resources provided by the Swedish National Infrastructure
for Computing (SNIC) at PDC.

@@

@@

\begin{tabular}{lrrrrrrrrr}
\toprule
{} &  $n$ &  $c$ &  $\nu $ &  $\epsilon$ &  $\frac{k_{diss}}{k_f}$ &   $F_f$ &  $\; Re$ &  $ReF_f^{2/3} $ &  $t_{\max}$ \\
\midrule
WL1  &  960 &   10 &   0.0985 &       0.998 &                    22.6 &   0.16 &  68.0 &           20 &          25 \\
WL2  & 1920 &   10 &   0.0492 &       0.985 &                    45.3 &    0.16 &  136 &           40 &          25 \\
WL3  & 2880 &   10 &   0.0328 &       0.984 &                    67.9 &    0.16 &    204 &           60 &          25 \\
WL4  & 3840 &   10 &   0.0246 &       0.993 &                    90.5 &   0.16 &   273 &            80 &          25 \\
WL5  & 7680 &   10 &   0.0123 &       1.000 &                     181 &   0.16 &   545 &           160 &          25 \\
WL6  &  960 &   20 &   0.0985 &       0.994 &                    22.6 &  0.08 &  68.1&            13 &          25 \\
WL7  & 2880 &   20 &   0.0328 &       0.982 &                    67.9 &    0.08 &  204 &           38 &          25 \\
WL8  &  960 &   40 &   0.0985 &       0.985 &                    22.6 &    0.04 &  68.0 &           8.0 &          25 \\
WL9  & 2880 &   40 &   0.0328 &       0.981 &                    67.9 &    0.04 &  204 &            24 &          25 \\
WL10 &  960 &  100 &   0.0985 &       0.976 &                    22.6 &   0.016 &  67.5 &            4.3 &          25 \\
WL11 & 2880 &  100 &   0.0328 &       0.961 &                    67.9 &  0.016 &  202 &           13 &          25 \\
WL12 &  960 &  200 &   0.0985 &       0.988 &                    22.6 & 0.0080 &  67.8 &          2.7 &          25 \\
WL13 & 2880 &  200 &   0.0328 &       0.928 &                    67.9 & 0.0079 &  200 &           7.9&          25 \\
\bottomrule
\end{tabular}

@@

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig15}}
\caption{$ \nabla \cdot {\bf u} $ for four different runs. Upper left: WL1, $ Re = 68 $, $ F_f = 0.16 $; Upper right: WL4,  $ Re = 273 $, $ F_f = 0.16 $; Lower left: WL12, $ Re = 68 $, $ F_f = 0.008 $; Lower right: WL13,  $ Re = 200 $, $ F_f = 0.008 $.}
\label{Physical_lap}
\end{figure}

The dynamics of the runs with Laplacian diffusion were similar to the runs with higher order diffusion. In figure \ref{MeanE2} we see mean energy in the stationary state versus $ c $ to the left and versus $ n $ to the right. 
The variation of mean energy with $ c $ seems to be a little bit weaker for these runs as compared to the runs with hyper diffusion. However, the series of runs with $ n = 2280 $ (green crosses) is pretty close to approaching the $ c^{1/2} $-scaling.
The variation of mean energy with resolution, or Reynolds number, is quite similar to what is seen in the corresponding plot \ref{MeanE}. For each $ c $ there is a monotonic increase of mean energy with resolution, and the increase is becoming stronger as $ c $ is increased, with comparable but not equal values of the exponent $ \alpha $.

In figure \ref{fig_distance_lap} we see the mean distance between the shocks as a function of $ F_f $, together with a straight line indicating $ F_f^{1/2} $. There is a reasonable agreement between $ F_f ^{1/2} $ and each of the two series of simulations at $ Re \approx 70 $ (blue dots) and $ Re \approx 200$ (yellow triangles). However, there is a gap between the two series. This gap may be explained by the fact that the shock detection algorithm is much more sensitive to the threshold value which is used for $ \nabla \cdot {\bf u} $ in these simulations than in the simulations with hyperviscosity.  In particular, this is true in the lower Reynolds number runs. In figure \ref{FlatnessDiv} we see the flatness of the divergence, multiplied by $ \nu $, versus $ F_f $. According to (\ref{FD}) we should have $ F_{\partial u} \nu \propto  d^{4/3} $ and if $ d \propto Fr^{1/2} $, the points should collapse on a single line, $ F_f^{2/3} $.  The three runs at highest $ Re $ and the lowest value of $ F_f $ fall on top of each other in the upper right corner, supporting the scaling $ \nu^{-1} $ in the high Reynolds number limit. For the three highest $ F_f $ there is a reasonable agreement with $ F_f^{2/3} $, although the lower Reynolds number runs (blue dots) fall below the higher Reynolds number runs, which we interpret as a low Reynolds number effect. The points corresponding to the two lowest values of $ F_f $ fall below the prediction. This can be explained by the fact that the shocks are on the verge of fading away in these runs. Clearly, a necessary condition for shocks to be present is that the mean distance between them is much larger than their  width, that is
\begin{equation} \label{Condition} 
\frac{d}{\delta x} \gg  1\, .
\end{equation} 
Since $ F_{\partial u} \propto d/\delta x $, this means that the flatness of divergence must be much larger than unity. Substituting (\ref{Width}) into (\ref{Condition})  and assuming that (\ref{MeanDistance}) is valid we can formulate the condition as
\begin{equation}  \label{SCond}
Re F_f^{2/3} \gg 1 \, .
\end{equation} 
If this condition is not fulfilled the shocks will fade away.  In figure \ref{Physical_lap} we have plotted the divergence for four different runs with different $ Re $ and $ F_f $. It should be pointed out again, that the area of the computational domain is sixteen times larger than area of the outcuts shown in the figures.  The two upper plots are from simulations with  $ F_f = 0.16 $ but different $ Re $ ($ Re = 68 $ to the left and $ Re = 273 $ to the right). As can be seen, the shocks are wider in the lower Reynolds number run to the left than in the higher Reynolds number run to the right, as expected. The lower left plot is from a simulation with the same $ Re $ as in the upper left plot, but with a much smaller $ F_f $. In this simulation we have $ Re F_f^{2/3} = 2.7 $, so the condition (\ref{SCond}) is not fulfilled, and the shocks have almost faded away. The lower right plot is from a simulation with the same $ F_f $ as in the lower left plot, but with a higher $ Re $. Here, $ Re F_f^{2/3} = 7.8 $ and  the shocks are clearly discernible.

>>>>

The shocks we observed in the SW simulations left us in a state of curiosity. In some simulations they appeared to be rather strong and in others rather weak. In some simulations they were densely packed and in others sparsely distributed.
In what way  do the input parameters regulate these variations? Will there always be shocks or will they disappear in the limit of weak nonlinearities?  Such questions made us to shift our theoretical focus and pursue the study, despite the fact that the answer to the question that originally motived it turned out to be negative.

@@

We have carried out a set of twenty forced-dissipative simulations of the SW
equations in a quadratic domain with periodic boundary conditions using the
standard open-source pseudo-spectral code FluidSim \cite[]{fluiddyn, fluidfft,
fluidsim}. In these twenty simulations we used an eight order diffusion operator to act as the agent of dissipation. 
 On the request from the reviewers we have also carried out a set of nineteen simulations with  Laplacian diffusion. The results from the latter set, which are similar to the results from the first set,  are presented in Appendix A.

@@

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig9}}
\caption{ Top: Flatness factor of transverse velocity increments. Bottom: Ratio between transverse and longitudinal flatness factor. Left: runs with $ n=3840 $: W3,
W7, W11,  W14 and W18. Right: runs with $ n = 7860 $: W4, W8 and W15.  The dotted straight lines indicate the value 1.5 predicted by the shock model.  }
\label{fig_flatness}
\end{figure}

@@

As expected, we have found that the displacement structure functions scale
exactly in the same way as the velocity structure functions, and for this reason we only plot
velocity structure functions. In figure~\ref{fig_StrucFunc} we see the
compensated and normalised second, fourth and sixth order longitudinal
structure functions from the five simulations with $ n = 3840 $ to the left and
the three simulations with $ n = 7860 $ to the right. At small separation, $ r
< \delta x $, the structure functions have the dependence $ \sim r^{p} $, which
is characteristic of a smooth velocity field, indicating that the shocks are
reasonably well resolved. There is a small bump around the shock width, $ r
\approx \delta x $, and at $ r > \delta x $, there is a range where the
compensated structure functions are flat, or almost flat. As expected, this
range is becoming broader for smaller $ c $ (or larger $ F_f $). The range is
also broader in the higher resolution runs to the right as compared to the
lower resolution simulations to the left. There is clearly a better collapse of
the curves for the sixth order structure functions compared to the second order
structure functions. This is not surprising, since the shock contribution to
the structure functions should become increasingly dominant with increasing
order. Plots of the transverse structure functions are very similar to the
plots of the longitudinal structure functions, with the difference that the
transverse structure functions are somewhat smoother at $ r \approx \delta x $.
In figure~\ref{fig_ratio} we see the ratio $ R_{p}(r) = \langle \mid \delta
u_L \mid ^{p} \rangle / \langle \mid \delta u_T \mid ^{p} \rangle$ for $ p=
2,3,4,5,6 $ from run W8, together with dotted straight lines, indicating the
values predicted by (\ref{Ratio}). As can be seen, there is a quite good
agreement with the predicted values in a limited range of separations, $ r >
\delta x $. Somewhat unexpectedly, the range in which there is a good agreement
becomes more narrow with increasing $ p $, an observation that we cannot
explain. It may also be noted that $ R_2 \rightarrow 3 $ in the limit of small
$ r $, which is the theoretical single point limit for an irrotational
isotropic field. In figure~\ref{fig_flatness} we see the flatness factor, $
F_T $, of the transverse structure functions at the top and the ratio, $
F_T/F_L $, at the bottom. The figures to the left show the results from the
five simulations with $ n = 3840 $ and the figures to the right show the
results from the three simulations with $ n = 7860 $. The flatness factor shows
increasingly large values for decreasing $ r $ with a dependence that is rather
close to but somewhat steeper than $ r^{-1} $. At small $ r $ the curves are
leveling out at very large values. For $ n = 7869 $ and $ c = 10 $ we see that
$ F_{T} \approx 400 $ at small $ r $. The degree to which the flatness factor
is increasing with decreasing scale is by some authors defined as the most
appropriate measure of spatial intermittency \cite[see for example][]{Frisch}.
If this measure is used, SW wave turbulence is, indeed, extremely intermittent.
In the two figures at the bottom we see that $ F_{T}/F_{L} \approx 1.5 $ in a
limited range of separations, $ r > \delta x $, which is becoming somewhat
broader as $ c $ is increasing and is also somewhat broader in the higher
resolution runs shown to the right as compared to the lower resolution runs
shown to the left. This is in accordance with the shock model predictions
(\ref{FL}) and (\ref{FT}).

@@

\vskip 0.3 cm

\noindent The authors would like to thank Gregory Falkovich and Sergey Nazarenko for  fruitful criticism of an early version of the manuscript, Sebastien Galtier for making a check of the final manuscript and three anonymous reviewers for useful comments. Financial
support from the Swedish Research Council (VR) is gratefully
acknowledged. The simulations were performed
on resources provided by the Swedish National Infrastructure
for Computing (SNIC) at PDC.

@@

\begin{tabular}{lrrrrrrrrr}
\toprule
{} &   $n$ &  $c$ &  $\nu_2$ &  $\epsilon$ &  $\frac{k_{diss}}{k_f}$ &   $F_f$ &  $Re$ &  $ReF_f^{2/3}$ &  $t_{\max}$ \\
\midrule
WL1  &   960 &   10 &   0.0985 &       0.998 &                    22.6 &   0.161 &  68.0 &           20.1 &          25 \\
WL2  &  1920 &   10 &   0.0492 &       0.985 &                    45.3 &   0.160 &   136 &           40.0 &          25 \\
WL3  &  2880 &   10 &   0.0328 &       0.984 &                    67.9 &   0.160 &   203 &           59.9 &          25 \\
WL4  &  3840 &   10 &   0.0246 &       0.993 &                    90.5 &   0.161 &   272 &           80.3 &          25 \\
WL5  &  7680 &   10 &   0.0123 &        1.00 &                     181 &   0.161 &   545 &            161 &          25 \\
WL6  &   960 &   20 &   0.0985 &       0.994 &                    22.6 &  0.0803 &  68.0 &           12.6 &          25 \\
WL7  &  2880 &   20 &   0.0328 &       0.982 &                    67.9 &  0.0800 &   203 &           37.7 &          25 \\
WL8  &  3840 &   20 &   0.0246 &       0.983 &                    90.5 &  0.0800 &   271 &           50.3 &          25 \\
WL9  &  7680 &   20 &   0.0123 &        1.00 &                     181 &  0.0805 &   545 &            102 &          25 \\
WL10 &   960 &   40 &   0.0985 &       0.985 &                    22.6 &  0.0400 &  67.7 &           7.93 &          25 \\
WL11 &  2880 &   40 &   0.0328 &       0.981 &                    67.9 &  0.0400 &   203 &           23.7 &          25 \\
WL12 &  3840 &   40 &   0.0246 &       0.978 &                    90.5 &  0.0399 &   270 &           31.6 &          25 \\
WL13 &  7680 &   40 &   0.0123 &       0.991 &                     181 &  0.0401 &   543 &           63.6 &          25 \\
WL14 &   960 &  100 &   0.0985 &       0.976 &                    22.6 &  0.0160 &  67.5 &           4.28 &          25 \\
WL15 &  2880 &  100 &   0.0328 &       0.961 &                    67.9 &  0.0159 &   202 &           12.7 &          25 \\
WL16 &  3840 &  100 &   0.0246 &       0.972 &                    90.5 &  0.0159 &   270 &           17.1 &          25 \\
WL17 &   960 &  200 &   0.0985 &       0.988 &                    22.6 & 0.00801 &  67.8 &           2.72 &          25 \\
WL18 &  2880 &  200 &   0.0328 &       0.928 &                    67.9 & 0.00785 &   199 &           7.87 &          25 \\
WL19 &  3840 &  200 &   0.0246 &       0.934 &                    90.5 & 0.00786 &   266 &           10.5 &          25 \\
\bottomrule
\end{tabular}

@@

@@

\begin{figure}
\centerline{\includegraphics[]{paper_04_shallow_water/Pyfig/fig15}}
\caption{$ \nabla \cdot {\bf u} $ for four different runs. Upper left: WL1, $ Re = 68 $, $ F_f = 0.16 $; Upper right:  { WL3,  $ Re = 203 $, $ F_f = 0.16 $;} Lower left: WL17, $ Re = 68 $, $ F_f = 0.008 $; Lower right: WL18,  $ Re = 199 $, $ F_f = 0.008 $.}
\label{Physical_lap}
\end{figure}

The dynamics of the runs with Laplacian diffusion were similar to the runs with higher order diffusion. In figure \ref{MeanE2} we see mean energy in the stationary state versus $ c $ to the left and versus $ n $ to the right. 
The variation of mean energy with $ c $ seems to be a little bit weaker for these runs as compared to the runs with hyper diffusion.  { However, the higher resolution runs are relatively close to approaching the $ c^{1/2} $-scaling.}
The variation of mean energy with resolution, or Reynolds number, is quite similar to what is seen in the corresponding plot \ref{MeanE}. For each $ c $ there is a monotonic increase of mean energy with resolution, and the increase is becoming stronger as $ c $ is increased, with comparable but not equal values of the exponent $ \alpha $.

In figure \ref{fig_distance_lap} we see the mean distance between the shocks as a function of $ F_f $, together with a straight line indicating $ F_f^{1/2} $. { As compared to the runs with hyperviscosity there is a larger spread of the points and the $ F_f^{1/2} $ scaling is not as clear. The lower Reynolds number series ($ Re \approx 70 $ blue dots) falls below the higher Reynolds number series. This may be explained by the fact that the shock detection algorithm is much more sensitive to the threshold value which is used for $ \nabla \cdot {\bf u} $ in these simulations than in the simulations with hyperviscosity.  In particular, this is true in the lower Reynolds number runs. } In figure \ref{FlatnessDiv} we see the flatness of the divergence, multiplied by $ \nu $, versus $ F_f $. According to (\ref{FD}) we should have $ F_{\partial u} \nu \propto  d^{4/3} $ and if $ d \propto Fr^{1/2} $, the points should collapse on a single line, $ F_f^{2/3} $.  {For the three largest $ F_f $, there is a relatively good collapse of the points from the three highest  Reynolds numbers series, supporting both the $ \nu^{-1} $-scaling and the $ F_f^{2/3} $-scaling. }
 The lower Reynolds number runs (blue dots) fall below the higher Reynolds number runs, which we interpret as a low Reynolds number effect. The points corresponding to the two lowest values of $ F_f $ fall below the prediction $ F_f^{2/3} $. This can be explained by the fact that the shocks are on the verge of fading away in these runs. Clearly, a necessary condition for shocks to be present is that the mean distance between them is much larger than their  width, that is
\begin{equation} \label{Condition} 
\frac{d}{\delta x} \gg  1\, .
\end{equation} 
Since $ F_{\partial u} \propto d/\delta x $, this means that the flatness of divergence must be much larger than unity. Substituting (\ref{Width}) into (\ref{Condition})  and assuming that (\ref{MeanDistance}) is valid we can formulate the condition as
\begin{equation}  \label{SCond}
Re F_f^{2/3} \gg 1 \, .
\end{equation} 
If this condition is not fulfilled the shocks will fade away.  In figure \ref{Physical_lap} we have plotted the divergence for four different runs with different $ Re $ and $ F_f $. It should be pointed out again, that the area of the computational domain is sixteen times larger than area of the outcuts shown in the figures.  The two upper plots are from simulations with  $ F_f = 0.16 $ but different $ Re $ ($ Re = 68 $ to the left and { $ Re = 203 $ } to the right). As can be seen, the shocks are wider in the lower Reynolds number run to the left than in the higher Reynolds number run to the right, as expected. The lower left plot is from a simulation with the same $ Re $ as in the upper left plot, but with a much smaller $ F_f $. In this simulation we have $ Re F_f^{2/3} = 2.7 $, so the condition (\ref{SCond}) is not fulfilled, and the shocks have almost faded away. The lower right plot is from a simulation with the same $ F_f $ as in the lower left plot, but with a higher $ Re = 199 $. Here, $ Re F_f^{2/3} = 7.8 $ and  the shocks are clearly discernible. { Comparing the two right plots with each other, they have approximately the same $ Re $, while the lower one has a considerably lower $ F_f $.  In this run the shocks are denser and straighter as compared to the higher $ F_f $-run.}
